LOINC2HPO_EPIC AND SCC

### 2022-04-22 code/r/MSDW_HPO_Phenotype_Analysis.Rmd
refactor

## GOAL
This is to LOINC2HPO analysis of both EPIC and SCC labs. 
```{r message=FALSE}
library(tidyverse)
library(glue)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('.db_credential.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), host='localhost', user=user, dbname = dbname, port = 2345, password=password)
```

@@

```{r}
CACHE_DIR = 'cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

@@

FORCE_RERUN <- FALSE
```

@@

patient_race_sex_distribution <- get_patient_race_sex_distribution(force_rerun = FALSE)

@@

For the directly tested phenotypes, we can observe what are the most tested abnormalities in one healthcare system. 
```{r}
tested_phenotype_rank_direct %>% head(10) %>% formattable::formattable()
```

>>>>

## GOAL
This is to LOINC2HPO analysis of both EPIC and SCC labs. 
```{r message=FALSE}
library(tidyverse)
library(glue)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
dsca <- DBI::dbConnect(RPostgres::Postgres(), 
                       host=Sys.getenv('DSCA_PHI_HOST'), 
                       dbname = Sys.getenv('DSCA_PHI_DBNAME'), 
                       port = Sys.getenv('DSCA_PHI_PORT'), 
                       user=Sys.getenv('DSCA_PHI_USERNAME'),
                       password= Sys.getenv('DSCA_PHI_PASSWORD'))
```

@@

```{r}
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

@@

# if true, ignore cached data and reconnect to database to get latest data;
# otherwise, use cached data first before trying to connect to database
FORCE_RERUN <- FALSE
```

@@

patient_race_sex_distribution <- get_patient_race_sex_distribution(force_rerun = FORCE_RERUN)

@@

For the directly tested phenotypes, we can observe what are the most tested abnormalities in one healthcare system. 
```{r}
tested_phenotype_rank_direct %>% head(10)
```
